An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/main.tex
Added results for method invariant by refinement

  - Assignment A:
    p1    = 0
    p2    = 0
    p3    = 1
    bit1  = 1
    nbit1 = 0
    q1    = 0
    q2    = 0
    q3    = 0
    q4    = 0
    q5    = 0
    nbit2 = 0

@@

  - Refinement constraint \delta:
    p2 + q3 + q5 + nbit1 + nbit2 >= 1
    ^    ^    ^    ^       ^
    |    |    |    |       |
    ------------------------
      |
      S = {p2, q3, q5, nbit1, nbit2}, therefore \delta excludes
      assignment A in the next iteration
\end{verbatim}

@@

    q1    > 0 => b_q1    = 1
    q1    = 0 => b_q1    = 0
    q2    > 0 => b_q2    = 1
    q2    = 0 => b_q2    = 0
    q3    > 0 => b_q3    = 1
    q3    = 0 => b_q3    = 0
    nbit2 > 0 => b_nbit2 = 1
    nbit2 = 0 => b_nbit2 = 0

@@

@@

    0        >=    a  - b
    0        >= (- a) + b

    a        <  target_1 + trap_1

    a        >= trap_1
    b        >= target_1
    nbit2    >= trap_1
    target_1 >= 0
    trap_1   >= 0

@@

    a        = 1
    b        = 1
    nbit2    = 1
    target_1 = 1
    trap_1   = 1

@@

    a     + nbit2 >= 1
    a + b + nbit2 <= 1
\end{verbatim}

>>>>

  - Assignment A:
    p1    = 0
    p2    = 0
    p3    = 1
    bit1  = 1
    nbit1 = 0
    q1    = 0
    q2    = 0
    q3    = 0
    q4    = 0
    q5    = 1
    nbit2 = 0

@@

  - Refinement constraint \delta:
    p2 + q2 + q3 + nbit1 + nbit2 >= 1
    ^    ^    ^    ^       ^
    |    |    |    |       |
    ------------------------
      |
      S = {p2, q2, q3, nbit1, nbit2}, therefore \delta excludes
      assignment A in the next iteration
\end{verbatim}

@@

    q1    > 0 => b_q1    = 1
    q1    = 0 => b_q1    = 0
    q2    > 0 => b_q2    = 1
    q2    = 0 => b_q2    = 0
    q3    > 0 => b_q3    = 1
    q3    = 0 => b_q3    = 0
    q4    > 0 => b_q4    = 1
    q4    = 0 => b_q4    = 0
    q5    > 0 => b_q5    = 1
    q5    = 0 => b_q5    = 0
    nbit2 > 0 => b_nbit2 = 1
    nbit2 = 0 => b_nbit2 = 0

@@

    b_p1     = 1
    b_p2     = 1
    b_p3     = 1
    b_bit1   = 0
    b_nbit1  = 0
    b_q1     = 0
    b_q2     = 0
    b_q3     = 0
    b_q4     = 0
    b_q5     = 0
    b_nbit2  = 0

@@

    p1 + q1 + nb1 + nb2 < 2 * target_1 + trap_1

    p1    >= 0
    p2    >= trap_1
    p3    >= target_1
    bit1  >= 0
    nbit1 >= trap_1
    q1    >= 0
    q2    >= trap_1
    q3    >= trap_1
    q4    >= 0
    q5    >= target_1
    nbit2 >= trap_1

    target_1 >= 0
    trap_1   >= 0

@@

    p1       = 0
    p2       = 1
    p3       = 1
    bit1     = 0
    nbit1    = 1
    q1       = 0
    q2       = 1
    q3       = 1
    q4       = 0
    q5       = 1
    nbit2    = 1
    target_1 = 1
    trap_1   = 1

@@

    p2        q2 + q3      + nbit1 + nbit2 >= 1
    p2 + p3 + q2 + q3 + q5 + nbit1 + nbit2 <= 2
